Pillar 1 - Sequential Pattern Mining

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
association rules with grades

```{r TODO}
# TODO: compute corrected confidence for AR
# TODO: compute lhs.support, for grade
```

@@

#
# Making transactions
transactions     <- make_transaction(item = item   )
transactions_PF  <- make_transaction(item = item_PF)
transactions_HL  <- make_transaction(item = item_HL)
#transactions_TNT <- make_transaction(data = d_transactions_not_taken, item = item_TNT)
transactions_TPF <- make_transaction(data = d_transactions_not_taken, item = item_TPF)
transactions_G   <- make_transaction(data = d_transactions_grade    , item = item_G  )

@@

      # Chosen parameters
      parameter = list(
        supp = 0,    # min support
        smax = 1,    # max support
        conf = 0,    # min confidence
        minlen = 2,  # min length of 
        maxlen = 2,  # max length of rule
        ext = TRUE,
        arem = "diff",
        aval = TRUE,
        minval = 0
        ),

@@

    # include rhs.support
    mutate(
      rhs_course = str_remove_all(rhs, pattern = "_fail|_low|_not taken")
      ) %>%
    left_join(
      select(data_support, item, !!type_rule_enquo),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = !!type_rule_enquo
      ) %>%
    select(
      - !!type_rule_enquo
      ) %>%

    # Editing output
    mutate_at(
      c("support", "lhs.support", "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, count, lhs.support,
      confidence, rhs.support,
      lift
    ) %>%
    arrange(
      desc(count)
    )

@@

  data %>%
    my_apriori(appearance = appearance) %>%
    clean_AR %>%
    compute_support(data_support = data_support, type_rule = !!enquo(type_rule))

@@

#
# AR low
AR_PF <- transactions_HL %>%
  make_AR(

@@

#
# AR not taken
AR_not_taken <- transactions_Taken %>%
  make_AR(

@@

# TODO

# AR_expanded_Grade <- my_apriori(transactions_expanded_Grade)

```
We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
     AR_expanded_Grade,
     file = "App/AR.RDATA")

# Remove objects
rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_Grade,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade,  
   AR_expanded_Grade)
```

>>>>

```{r TODO}
# TODO: compute corrected confidence for AR
# TODO: support of AR_TFP
```

@@

#
# Making transactions
transactions     <- make_transaction(item = item   )
transactions_PF  <- make_transaction(item = item_PF)
transactions_HL  <- make_transaction(item = item_HL)
transactions_TNT <- make_transaction(data = d_transactions_not_taken, item = item_TNT)
transactions_TPF <- make_transaction(data = d_transactions_not_taken, item = item_TPF)
transactions_G   <- make_transaction(data = d_transactions_grade    , item = item_G  )

@@

      # Chosen parameters
      parameter = list(
        supp = 0,    # min support
        smax = 1,    # max support
        conf = 0,    # min confidence
        minlen = 2,  # min length of 
        maxlen = 2,  # max length of rule
        ext = TRUE
        ),

@@

    # include rhs.support
    mutate(
      rhs_course = str_remove_all(rhs, pattern = "_fail|_low|_not taken")
      ) %>%
    left_join(
      select(data_support, item, !!type_rule_enquo),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = !!type_rule_enquo
      ) %>%
    select(
      - !!type_rule_enquo
      )

```{r editing_AR}
editing_AR <- function(AR){

  AR %>%
    mutate_at(
      c("support", "lhs.support", 
        "confidence", "rhs.support",
        "lift"
        ),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, count, lhs.support,
      confidence, rhs.support,
      lift
    ) %>%
    arrange(
      desc(count)
    )

@@

  data %>%
    my_apriori(appearance = appearance) %>%
    clean_AR %>%
    compute_support(
      data_support = data_support,
      type_rule = !!enquo(type_rule)
      ) %>%
    editing_AR

@@

#
# AR low
AR_HL <- transactions_HL %>%
  make_AR(

@@

#
# AR not taken
AR_TNT <- transactions_TNT %>%
  make_AR(

@@

#
# AR not taken / fail / pass

AR_TPF <- transactions_TPF %>%
  make_AR(

    # impose lhs and rhs to be not taken
    appearance = list(
      rhs = d_transactions_not_taken %>%
        filter(TPF == "fail") %>%
        distinct(`item_TPF`) %>%
        pull
    ),

```{r AR grade (by hand)}

#
# d_support
d_support_grade <- d_support %>%
  gather(
    key   = grade_round,
    value = support.grade,
    rate.0, rate.1, rate.2, rate.3, rate.4, rate.5, rate.6, rate.7, rate.8, rate.9, rate.10
    ) %>%
  mutate( 
    grade_round = substr(grade_round, start = 6, stop = 7),
    grade_round = as.numeric(grade_round)
    ) %>%
  select(-c(rate.fail, rate.low))

# Make RA
AR_G <- transactions_G %>%
  my_apriori(appearance = NULL) %>%
  clean_AR %>%

  # include lhs.support by hand
  separate(
    lhs, 
    into = c("lhs_course", "lhs_grade_round"), 
    sep = "_",
    remove = FALSE,
    convert = TRUE
    ) %>%
  left_join(
    d_support_grade,
    by = c("lhs_course" = "item", "lhs_grade_round" = "grade_round")
    ) %>%
  mutate(
    lhs.support = support.grade
    ) %>%
  select(
    - support.grade
    ) %>%

  # include rhs.support by hand
  separate(
    rhs, 
    into = c("rhs_course", "rhs_grade_round"), 
    sep = "_",
    remove = FALSE,
    convert = TRUE
    ) %>%
  left_join(
    d_support_grade,
    by = c("rhs_course" = "item", "rhs_grade_round" = "grade_round")
    ) %>%
  mutate(
    rhs.support = support.grade
    ) %>%
  select(
    - support.grade
    ) %>%

    editing_AR

We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_TNT, AR_TPF, AR_G,
     file = "App/AR.RDATA")

# Remove objects
rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_G,
   AR_taken, AR_PF, AR_HL, AR_TNT, AR_G)
```
